Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-22 prop_letter.tex
prop_letter.tex Updating...

In other words, any density matrix~$\rho$ defines a quantum probability
measure~$\mu_{\rho}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
where $\events$ is the set of all projectors in a Hilbert space~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}.
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
which should satisfy:
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}
\end{itemize}
Gleason's theorem asserts that there exists a unique mixed state~$\rho$
such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.

@@

In order to model the idea of finite precision measurement, we replace
the range of $\mu$ from the infinity precision~$[0,1]$ to a collection
of finite number of intervals~$\mathscr{I}$, and consider a quantum
IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. It is intuitive
to consider $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
and 
\begin{equation}
[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
\end{equation}
 so that $\bar{\mu}$ satisfy the follow conditions:
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
to inclusion. This becomes intuitive if we plug in Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
into Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
The left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
and the right-hand side becomes $\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$
which is a proper superset of $\left[1,1\right]$ when $r>l$.

Although considering IVPM is new for quantum, people have already
defined classical IVPMs~\cite{JamisonLodwick2004}. We find if we
restrict on a mutually commuting sub-event space~$\events'\subseteq\events$,
quantum IVPMs are one-to-one corresponding to the classical ones.
Despite restricting on the domain of quantum IVPMs, if we pick the
range as a limiting case, the collection of all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
then quantum IVPMs becomes real-valued probability measures which
case Gleason's theorem applies. In the next paragraph, we will show
the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA} is another limit case when the collection
of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

>>>>

In other words, any density matrix~$\rho$ can define a function
$\mu_{\rho}^{\mathrm{\mathrm{B}}}$ from the set of all projectors
in a Hilbert space~$\events$ to $[0,1]$. This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$
is called a quantum probability measure because it satisfies the following
probability axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
\begin{itemize}
\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{0})=0$. 
\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{1})=1$. 
\item For any projection $P$, $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\mathbb{1}-P\right)=1-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}
\end{itemize}
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
satisfying the above conditions, Gleason's theorem asserts that there
exists a unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
in a Hilbert space of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.

@@

In order to model the idea of finite precision measurement, we replace
the infinity precision~$[0,1]$ by a collection of finite number
of intervals~$\mathscr{I}$, and consider quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
It is intuitive to require $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
and 
\begin{equation}
[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
\end{equation}
so that $\bar{\mu}$ satisfy the follow interval-valued probability
axioms: 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
to inclusion because the equality is usually too strong to hold. For
example, if we plug in Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement})
into Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
the left-hand side becomes $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
and the right-hand side becomes $\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$
which is a proper superset of $\left[1,1\right]$ when $r>l$.

Although considering IVPM is new for quantum, people have already
defined classical IVPMs~\citep{JamisonLodwick2004}. If we restrict
quantum IVPMs~$\bar{\mu}:\events\rightarrow\mathscr{I}$ on a mutually
commuting sub-event space~$\events'\subseteq\events$, every restricted
quantum IVPM~$\bar{\mu}\mid_{\events'}$ is one-to-one corresponding
to a classical one.

On the other hand, Gleason's theorem can be expressed as the limit
case when the collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
In the next paragraph, we will show the Kochen-Specker theorem~\citep{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
is another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}
